IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/intro.tex
condensation
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

A further benefit of the coarse-grained approach
is that a single IFC design and semantics can be generalized
to a large class of programming languages.
Leveraging this insight, we define a general form of coarse-grained
dynamic IFC and show how IFC can be combined with \emph{any} programming
language conforming to a general semantic framework.
At the core of our IFC system is a sandboxing construct that isolates
potentially sensitive computations, allowing them to
communicate only through clearly specified interfaces.
Based on a framework for combining the operational semantics
of our core IFC calculus with the operational semantics of any target language,
we formally state and prove non-interference guarantees that are
independent of the choice of specific target language.

>>>>

A further benefit of the coarse-grained approach
is that a single IFC design and semantics can be generalized
to a large class of programming languages.
Leveraging this insight, we define a general form of coarse-grained
dynamic IFC and show how it can be combined with \emph{any} programming
language conforming to a general semantic framework.
At the core of our IFC system is a sandboxing construct that isolates
potentially sensitive computations, allowing them to
communicate only through clearly specified interfaces.
Using the Matthews-Findler approach~\cite{Matthews:2007:OSM:1190216.1190220}
for combining operational semantics,
we formally state and prove non-interference guarantees that are
independent of the choice of specific target language.
